---
title: "week5 case1 extra"
output: html_notebook
---

## Generate 2 random data groups and do F test.
* Brand A: 10 random data
    * mean = 3.1
    * standard deviation = 0.5
* Brand B: 8 random data
    * mean = 2.7
    * standard deviation = 0.7

```{r}
sample = 11
conf = 0.98

a = rnorm(10*sample, 3.1, 0.5)
b = rnorm(8*sample, 2.7, 0.7)

ahist = hist(a)
par(new=T)
curve(
  dnorm(x, 3,1, 0.5),
  xlim=c(
    min(ahist$breaks), 
    max(ahist$breaks)
  ),
  axes=F, xlab="", ylab=""
)

bhist = hist(b)
par(new=T)
curve(
  dnorm(x, 2.7, 0.7),
  xlim=c(
    min(bhist$breaks), 
    max(bhist$breaks)
  ),
  axes=F, xlab="", ylab=""
)

var.test(a, b, conf.level=conf)
var.test(b, a, conf.level=conf)
```
```{r}
## T test to estimate population of A
reta = t.test(a, conf.level=0.98)
print(reta)
inta1 = as.double(reta$estimate) - sqrt(as.double(reta$conf.int[2]))
inta2 = as.double(reta$estimate) + sqrt(as.double(reta$conf.int[2]))
```
A nicotin contents interval in 98% confident with 1 sigma is  
`r inta1` to `r inta2`

```{r}
## T test to estimate population of B
retb = t.test(b, conf.level=0.98)
print(retb)
intb1 = as.double(retb$estimate) - sqrt(as.double(retb$conf.int[2]))
intb2 = as.double(retb$estimate) + sqrt(as.double(retb$conf.int[2]))
```
B nicotin contents interval in 98% confident with 1 sigma is  
`r intb1` to `r intb2`

## Conclusion
F test indicates variance between Brand A and B is not equal.   
Indicated P values are too small than significant level, 2%.

```{r fig.width=7.5}
par(mar=c(5,4,4,5))
curve(
  dnorm(x, 3.1, 0.5), 
  xlim=c(0, 7), col=2, ylab=""
)

par(new=T)
curve(
  dnorm(x, 2.7, 0.7),
  xlim=c(0, 7), col=3, axes=F, ylab=""
)

par(new=T)
curve(
  df(x, 9, 7),
  xlim=c(0, 7), axes=F, ylab=""
)

par(xpd=T)
legend(
  par()$usr[2], par()$usr[4],
  legend=c("F", "A", "B"),
  pch=20, col=1:3
)
```
