---
title: "Week5 case1A"
output: html_notebook
---
> A study has been made to compare the nicotine contents of two brand of cigarettes.
 10 cigarettes of brand A had an average nicotine content of 3.1 milligrams with standard deviation of 0.5 milligrams, while 8 cigarettes of brand B had an average nicotine contents  of 2.7 milligrams with standard deviation of 0.7 milligrams. Assuming that two sets of data are independent random samples from normal populations.

> 1. Using F distribution and interval approach, Evaluate the scatterings of nicotine of brand A is always smaller than brand B or not. (assuming 98% confidence interval)

### Premise
* U and V are independent...
* U = Brand A
* V = Brand B   
Values of A are a numeratoir, and values of B are a denominator.

```{r setup}
mat = matrix(c(10, 3.1, 0.5), ncol=3)
mat = rbind(mat, c(8, 2.7, 0.7))
rownames(mat) = c("A", "B")
colnames(mat) = c("freedom", "mean", "stddev")

varA = mat["A", "stddev"] ^ 2
varB = mat["B", "stddev"] ^ 2
dfA = mat["A", "freedom"]-1
dfB = mat["B", "freedom"]-1
crtc = 0.02
conf = 1 - crtc
F1 = qf(crtc/2, dfA, dfB)
F99 = qf(1-crtc/2, dfA, dfB)

seekInterval = function(s1, s2, f){
  return(s1/s2*1/f)
}
```

### Parameters
`r data.frame(print(mat))`
* A variance = `r varA`
* B variance = `r varB`
* F at 1% = `r F1`
* F at 99% = `r F99`
```{r}
i2 = seekInterval(varA, varB, F1)
i1 = seekInterval(varA, varB, F99)
```
* interval bottom = `r i1`
* interval top = `r i2`

### Premise
* the scatterings of nicotine = true variable of nicotine.
* `r i1` < ""A true variance / B true variance"" < `r i2` must be true.

### Assumption 1: When B true variance = `r varB`
A true variance > `r i1` * `r varB`   
A true variance > `r i1 * varB`

A true variance < `r i2` * `r varB`    
A true variance < `r i2 * varB`

`r i1 * varB` < A true variance < `r i2 * varB`

#### A true nicotine contents (1 sigma in interval top)
* B sample = `r mat["B", "mean"] + sqrt(varB)`
* 
`r mat["A", "mean"] + sqrt(i1 * varB)` < A < `r mat["A", "mean"] + sqrt(i2 * varB)`

#### Conclusion
FALSE --> the scatterings of nicotine of brand A is always smaller than brand B.    
FALSE --> the scatterings of nicotine of brand A is NOT always smaller than brand B.

***
### Assumption 2: When A true variance = `r varA`
B true variance < `r varA` / `r i1`   
B true variance < `r varA / i1`   

B true variance > `r varA` / `r i2`   
B true variance > `r varA / i2`

`r varA / i2` < B true variance < `r varA / i1`

#### B true nicotine contents (1 sigma in interval top)
* A sample = `r mat["A", "mean"] + sqrt(varA)`
* 
`r mat["B", "mean"] + sqrt(varA / i2)` < B < `r mat["B", "mean"] + sqrt(varA / i1)`

#### Conclusion
FALSE --> the scatterings of nicotine of brand A is always smaller than brand B.   
FALSE --> the scatterings of nicotine of brand A is NOT always smaller than brand B.

***
```{r fig.width=7.5}
par(mar=c(5,4,4,5))
curve(dnorm(x, mat["A", "mean"], mat["A", "stddev"]), xlim=c(0, 7), col=2, ylab="")
par(new=T)
curve(
  dnorm(x, mat["B", "mean"], mat["B", "stddev"]),
  xlim=c(0, 7), col=3, axes=F, ylab=""
)
par(xpd=T)
legend(par()$usr[2], par()$usr[4], legend=rownames(mat), pch=20, col=2:3)
par(new=T)
curve(
  df(x, dfA, dfB),
  xlim=c(0, 7), axes=F, ylab=""
)
abline(v=F1, col=4)
abline(v=F99, col=4)
```
98% interval is between blues.